### 2018-05-26 background.tex
fix syntax error

The main memory, $NL$ levels of caches, and $NT$ processor cores
forming a memory hierarchy are generally organized in terms
of an $NL+2$ level regular tree structure.
The processor cores at level $0$ are leaves,
the caches at levels $1$ -- $NL$ are intermediate nodes,
and the main memory at level $NL+1$ is the tree root.
Any node in the memory hierarchy can be identified by
its layer and its unique index at the layer $(layer, index)$.
The number of nodes at layer $l$ is $NT / nt_l$.

>>>>

The main memory, $NL$ levels of caches, and $NT$ processor cores
form a memory hierarchy which are generally organized in terms
of an $NL+2$ level regular tree structure.
The processor cores at level $0$ are leaves,
the caches at levels $1$ -- $NL$ are intermediate nodes,
and the main memory at level $NL+1$ is the tree root.
Any node in the memory hierarchy can be identified by
its layer and its unique index at the layer $(layer, index)$.
The number of nodes at layer $l$ is $NT / nt_l$.
